<NAME> - an analyser framework for P4

### 2021-03-23 publications/The_tool_intro/paper.tex
pub: add orcid
pub: 6 page, captions

	\section{Analysis framework}

Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR.  
Modular compilers like P4C~\cite{p4c} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler. Moreover, P4C allows getting information from older states of the IR, as each transformation pass returns an immutable IR instance.
Even here, the three-fold separation of frontend-midend-backend have to remain: in order satisfy midend-dependencies, and subsequently, backend-dependencies, the backend must sequentially execute the frontend, the midend, and finally its own passes.

@@

\subsection{Representation - Architecture}\label{sec:rep} % 4 hasáb - Dániel
	% belső gráf, a koncepció
	% elemzések
	% app megvalósítás

  \begin{figure}
    \includegraphics[width=0.18\textwidth]{figures/arch-top.pdf}
    \caption{TODO}\label{fig:arch-top}
  \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.3\textwidth]{figures/arch-deps.pdf}
    \caption{TODO}\label{fig:arch-deps}
  \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.45\textwidth]{figures/output.pdf}
    \caption{TODO}\label{fig:output}
  \end{figure}

>>>>

	\section{Analysis framework}
Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR.  
Modular compilers like the P4 reference compiler P4C\footnote{\url{https://github.com/p4lang/p4c}} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler. Moreover, P4C allows getting information from older states of the IR, as each transformation pass returns an immutable IR instance.
Even here, the three-fold separation of frontend-midend-backend have to remain: in order satisfy midend-dependencies, and subsequently, backend-dependencies, the backend must sequentially execute the frontend, the midend, and finally its own passes.

@@

\clearpage

\subsection{Tool architecture}\label{sec:rep} % 4 hasáb - Dániel
	% belső gráf, a koncepció
	% elemzések
	% app megvalósítás

  \begin{figure}
    \includegraphics[width=0.18\textwidth]{figures/arch-top.pdf}
    \caption{High-level view of the tool architecture}\label{fig:arch-top}
  \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.3\textwidth]{figures/arch-deps.pdf}
    \caption{Expanded view of the architecture layers}\label{fig:arch-deps}
  \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.42\textwidth]{figures/output.pdf}
    \caption{Knowledge graph excerpt of the Figure~\ref{code:P4} code}\label{fig:output}
  \end{figure}
